---
title: "STAT585_Lab3_Group12"
author: "Weiquan LUO, Kellie MCCLERNON, Hao WANG"
date: "3/24 /2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here is a link to our GitHub [repository](https://github.com/WeiquanLuo/lab3team12)

Here is a link to our [package main page](https://haowang47.github.io/lab3team12.html)

## Package installation
```{r, eval=F}
devtools::install_github("WeiquanLuo/lab3team12")
```

## Load package
```{r, eval=F}
library(lab3team12)
```

## Functions

### `team_5`

The `team_5` function was written by Kellie. It was created based on the solution for lab2 by group 5.

The function has two input values.

- `file`:	This is the shape file with .shp extension that will be converted to a dataframe. It is a file path in the form of a character string (ends in .shp).
- `tolerance`: This controls how much the shape file is thinned. The default is 0.1.

### `team_10`

The `team_10` function was written by Hao. It was created based on the solution for lab2 by group 10.

The function has two input values.

- `file`:	This is the shape file with .shp extension that will be converted to a dataframe. It is a file path in the form of a character string (ends in .shp).
- `tolerance`: This controls how much the shape file is thinned. The default is 0.1.

### `team_11`

The `team_11` function was written by Weiquan. It was created based on the solution for lab2 by group 11.

The function has two input values.

- `x`:	This is the list object (read by read_sf from package `sf`), which is originally a shape file with .shp extension. team_11 function will convert it to a dataframe 
- `tolerance`: This controls how much the shape file is thinned. The default is 0.1.

## Example

Example shape file downloaded from [gdam](https://gadm.org/download_country_v3.html).

```{r, eval=F}
file=system.file("extdata", "gadm36_AUS_1.shp", package = "lab3team12")
tmp=team_5(file)

# or
tmp=team_10(file)

# or 
tmp=sf::read_sf(file)
tmp=team_11(tmp)
  
# plot 
library(ggplot2)
ggplot(tmp, aes(x=long,y=lat,group=group))+geom_polygon()
```
